\section{Categories}
    \begin{definition}
        A \textbf{category} $\catc$ consists of
        \begin{enumerate}
            \item a collection of objects $\ob{\catc}$
            \item for each $A,B\in\ob{\catc}$ a collection of morphisms $\homc{\catc}{A}{B}$ called the hom-set of $A$ and $B$\\
            We will write $f : A\to B$ or
$\begin{tikzcd}
	A & B
	\arrow["f", from=1-1, to=1-2]
\end{tikzcd}$ for $f\in\homc{\catc}{A}{B}$
            \item for each $A,B,C\in\ob{\catc}$ a map $\circ$ : $\homc{\catc}{A}{B}\times\homc{\catc}{B}{C}\to \homc{\catc}{A}{C}$ such that
        for morphisms $\begin{tikzcd}
            A & B & C & D
            \arrow["f", from=1-1, to=1-2]
            \arrow["g", from=1-2, to=1-3]
            \arrow["h", from=1-3, to=1-4]
        \end{tikzcd}$ we have $h\circ(g\circ f) = (h\circ g)\circ f$
            \item for each object $A\in\ob{\catc}$ we have a morphism $1_A : A\to A$ satisfying
             for all morphisms $\begin{tikzcd}
                X & A & Y
                \arrow["f", from=1-1, to=1-2]
                \arrow["g", from=1-2, to=1-3]
            \end{tikzcd}$ the identity
            \begin{equation}\label{ideq}1_A \circ f = f \hspace{20pt} g \circ 1_A = g\end{equation}
            which we will call the identity morphism. 
        \end{enumerate}
    \end{definition}
\begin{remark}
    From \eqref{ideq} it follows that the identity morphism $1_A$ is unique, since for $1_A,\hat{1}_A$ we have
    \[1_A = 1_A\circ \hat{1}_A = \hat{1}_A\]
\end{remark}
\begin{definition}
    Let $\catc$ and $\catd$ be categories. We will say that $\catc$ is a \textbf{subcategory} of $\catd$, if 
    $\ob{\catc}$ is a subcollection of $\ob{\catd}$, for each $A,B\in\ob{\catc}$ the hom-set
    $\homc{\catc}{A}{B}$ is a subcollection of $\homc{\catd}{A}{B}$, the identity morphisms in $\catc$ are 
    the identity morphisms in $\catd$ and the composition $\circ$ in $\catc$ is the restriction of composition in $\catd$.
    If $\forall A,B\in\ob{\catc} : \homc{\catc}{A}{B} = \homc{\catd}{A}{B}$
    then we call $\catc$ a \textbf{full subcategory} of $\catd$.
\end{definition}
\begin{definition}
    A category $\catc$ is called \textbf{locally small} if all of the hom-sets in $\catc$ are sets. 
    A category $\catc$ is \textbf{small} if it is locally small and $\ob{\catc}$ is a set.
\end{definition}
\begin{definition}
    For a category $\catc$ we define the \textbf{opposite category} $\opp{\catc}$ by
    \[\ob{\opp{\catc}} = \ob{\catc}\]
    \[\homc{\opp{\catc}}{A}{B} = \homc{\catc}{B}{A}\]
    For $A,B,C\in\ob{\opp{\catc}}$ and morphisms $\begin{tikzcd}
	A & B & C
	\arrow["f", from=1-1, to=1-2]
	\arrow["g", from=1-2, to=1-3]
\end{tikzcd}$ we'll let $g\circop f = f\circ g$ and define the identity morphisms of $\opp{\catc}$ as the identity morphisms of $\catc$.
\end{definition}
The opposite category is a category since 
\[
    h\circop (g\circop f) = (g\circop f) \circ h = (f \circ g) \circ h = f\circ (g\circ h) = (g\circ h)\circop f = (h\circop g)\circop f
\]
and 
\[
    g\circop 1_A = 1_A \circ g = g \hspace{20pt} 1_A\circop f = f\circ 1_A = f
\]
\begin{definition}
    Let $\catc$ be a category and $f: A\to B$ a morphism in $\catc$. We call $f$ an \textbf{isomorphism}, if
    there exists $g: B\to A$, such that $f\circ g = 1_B$ and $g\circ f = 1_A$.\par
    We call $f:A\to B$ a \textbf{split monomorphism} if there exists $g:B\to A$, such that
    $g\circ f = 1_A$ and similarly $f$ is a \textbf{split epimorphism} if there exists $g:B\to A$, such that
    $f\circ g = 1_B$.
\end{definition}
\begin{remark}
    Note that if $f$ is an isomorphism, then the inverse morphism $g$ is unique and that
    $f$ is an isomorphism if and only if it is both a split epimorphism and a split monomorphism.
\end{remark}
\begin{definition}
    Let $\catc$ and $\catd$ be categories. A \textbf{(covariant) functor} $F: \catc \to \catd$ consists of 
    \begin{enumerate}
        \item \textcolor{red}{a map} $\ob{\catc}\to\ob{\catd}$ assigning $A \mapsto F(A)$
        \item for each $A,B\in\ob{\catc}$ \textcolor{red}{a map} $\homc{\catc}{A}{B}\to\homc{\catd}{F(A)}{F(B)}$ which assigns $f \mapsto F(f)$
    \end{enumerate}
    such that it preserves composition $F(g\circ f) = F(g)\circ F(f)$ and the identity $F(1_A) = 1_{F(A)}$.\\ We define a \textbf{contravariant functor} $F:\catc \to \catd$ to 
    be just a covariant functor $F:\opp{\catc} \to \catd$.
\end{definition}
\begin{definition}
    Let $F: \catc \to \catd$ be a functor. We call $F$ \textbf{faithful}, if it is injective on hom-sets. 
    More precisely for all $A,B\in\ob{\catc}$ and each pair of morphisms $\begin{tikzcd}
        A & B
        \arrow["g"', shift right, from=1-1, to=1-2]
        \arrow["f", shift left, from=1-1, to=1-2]
    \end{tikzcd}$ if $F(f)=F(g)$ then $f=g$.\\ 
    We say that $F$ is \textbf{full} if it is surjective on hom-sets.
    So for all $A,B\in\ob{C}$ and $g: F(A)\to F(B)$ there exists $f:A\to B$ such that $F(f)=g$.
\end{definition}
\begin{remark}
    Note that the definition doesn't say anything about the map on objects being injective or surjective,
    nor does it say that if the images of any two morphisms are equal then they are the same, since
    the functor may map the morphisms between two different objects to the same morphism in the target category.
\end{remark}
\input{naturaltrans.tex}
\begin{definition}
    Let $\catc$ be a category and choose $X\in\ob{\catc}$. We define the \textbf{slice category $\catc$ over $X$} denoted as $\catc /X$,
    whose objects are pairs $(A,f)$ where $A\in\ob{\catc}$, $f: A \to X$ and whose morphisms 
    $g: (A,f_1) \to (B,f_2)$ are just morphisms $g:A\to B$ in $\catc$ such that the following diagram commutes
\[\begin{tikzcd}
	A && B \\
	& X
	\arrow["g", from=1-1, to=1-3]
	\arrow["{f_1}", from=1-1, to=2-2]
	\arrow["{f_2}"', from=1-3, to=2-2]
\end{tikzcd}\]
    Notice that composition of two morphisms $\catc /X$ yields again a morphisms in $\catc /X$
    since when the two triangles in the left diagram below commute then the entire square commutes as well
    and that by the very definition of identity morphism the triangle on the right side below commutes 
\[\begin{tikzcd}
	& B &&& A && A \\
	A && C \\
	& X &&&& X
	\arrow["{g_2}", from=1-2, to=2-3]
	\arrow["{f_2}"{description}, from=1-2, to=3-2]
	\arrow["{1_A}", from=1-5, to=1-7]
	\arrow["{f_1}"', from=1-5, to=3-6]
	\arrow["{f_1}", from=1-7, to=3-6]
	\arrow["{g_1}", from=2-1, to=1-2]
	\arrow["{f_1}"', from=2-1, to=3-2]
	\arrow["{f_3}", from=2-3, to=3-2]
\end{tikzcd}\]
\end{definition}
\begin{definition}
    Given two objects $A,B$ their coproduct is an object $U$ with 
    two morphisms $\iota_A: A \to U$ and $\iota_B: B \to U$, such
    that for any other triple $(U^\prime,f: A\to U^\prime,g: A\to U^\prime)$
    there exists a unique morphism $f+g: U\to U^\prime$, such that the following diagram commutes
\[\begin{tikzcd}
	& {U^\prime} \\
	\\
	A & U & B
	\arrow["f", from=3-1, to=1-2]
	\arrow["{\iota_A}", from=3-1, to=3-2]
	\arrow["{f+g}"{description}, from=3-2, to=1-2]
	\arrow["g"', from=3-3, to=1-2]
	\arrow["{\iota_B}"', from=3-3, to=3-2]
\end{tikzcd}\]
\end{definition}
\begin{proposition}
    Coproduct $U$ is unique up to an isomorphism.
\end{proposition}
\input{extensivity.tex}